$p$-adic precision

### 2014-02-10 padicprec.tex
Improvement of the locally analytic part

\begin{prop}\label{prop:locanalytic}
Let $E$ and $F$ be two complete normed $K$-vector spaces, and let $f$ be locally analytic map $E \rightarrow F$.  Let $x \in E$, and let $f(x+h)=f(x)+\sum_{k \geq 0}^{+\infty} L_k \cdot (h,\dots,h)$ be the power series development of $f$ at $x$. We assume $L_1$ is surjective. 
Let $C$ be given by the Banach-Schauder theorem for $L_1$, $\varepsilon = \frac{1}{C}$. 
Let $F(t) = \sum_{k\geq 0}^{+\infty} \interleave L^{k+1}(0) \interleave  t^k \in \mathbb{R}[[t]]$, let $NP_F$ be its Newton polygon.
Let $\mu$ be the slope of the line passing by $(0, \log_p \varepsilon)$ and tangent to $NP_F$.
Then $r$ such that $\mu=\log_p r$ is enough for lemma \ref{lem:main}.
\end{prop}
\begin{proof}
Let us assume that $x=0$, $f(0)=0$, and for $r>0$, $f(x)=L_1 \cdot x +\sum_{n \geq 2} L_n \cdot (x, \dots,x)$ is the Taylor serie expansion of $f$ at $0$, coinciding on $B_E (0,r)$.

>>>>

\begin{deftn}\label{deftn:analyticNP}
Let $E$ and $F$ be two complete normed $K$-vector spaces, and let $f$ be locally analytic map $E \rightarrow F$.  Let $x \in E$, and let $f(x+h)=f(x)+\sum_{k \geq 0}^{+\infty} L_k \cdot (h,\dots,h)$ be the power series development of $f$ at $x$.
Let $F(t) = \sum_{k\geq 0}^{+\infty} \interleave L^{k+1}(x) \interleave  t^k \in \mathbb{R}[[t]].$

We define $NP(f,x)$ to be the function defined by its Newton polygon, the lower convex hull of the $(k,\log ( \interleave L^{k+1}(x) \interleave)),$ with $k \geq 0.$
\end{deftn}

We now prove that the knowledge of $NP(f,x)$ is enough to recover $\delta$.

\begin{prop}\label{prop:locanalytic}
Let $E$ and $F$ be two complete normed $K$-vector spaces, and let $f$ and the $L_k$'s be as in definition \ref{deftn:analyticNP}. We assume $L_1$ is surjective. 
Let $C$ be given by the Banach-Schauder theorem for $L_1$, $\varepsilon = \frac{1}{C}$. 
Let $\mu$ be the slope of the line passing by $(0, \log_p \varepsilon)$ and tangent to $NP(f,x)$.
Then $r$ such that $\mu=\log_p r$ is enough for lemma \ref{lem:main}.
\end{prop}
\begin{proof}
Let us assume that $x=0$, $f(0)=0$, and for $r>0$, $f(x)=L_1 \cdot x +\sum_{n \geq 2} L_n \cdot (x, \dots,x)$ is the Taylor serie expansion of $f$ at $0$, coinciding on $B_E (0,r)$.
